% Nathan J. Goldbaum - Curriculum Vitae
%
% This is based on a template, http://jblevins.org/projects/cv-template/
% original copyright notice below.
%
% Copyright (C) 2004-2016 Jason R. Blevins <jrblevin@sdf.org>
% http://jblevins.org/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage[compact]{titlesec}
\usepackage{mdwlist}
\usepackage{tabularx}
\usepackage{fancyhdr}

% Fonts
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% Set your name here
\def\name{Nathan J. Goldbaum}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {astrophysics, open source, visualization, python},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={7.0in, 9.0in},
  left=0.75in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}

\sectionfont{\rmfamily\bfseries\Large}
\subsectionfont{\rmfamily\bfseries\itshape\large}  %chktex 6

% Don't indent paragraphs.
\setlength\parindent{0em}

\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}

\newcommand{\textline}[2]{
  \begin{tabularx}{\textwidth}{XY}
  #1 & #2
  \end{tabularx}
}

\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\setcounter{footnote}{1}

\renewcommand{\labelitemii}{$\bullet$}

\setlist[1]{leftmargin=0.5em, itemsep=0.4em, parsep=0em, topsep=0.25em, partopsep=0pt}
\setlist[2]{leftmargin=3em, itemsep=0.5em, parsep=0em, topsep=0.25em, partopsep=0pt}


\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[R]{Last updated: \today}
\pagestyle{fancy}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.6\textwidth}
  2770 JT Coffman Dr \\
  Champaign, IL 61822
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
  Phone: (720) 201-2231 \\  %chktex 8
  Email: \href{mailto:nathan12343@gmail.com}{nathan12343@gmail.com} \\
  Homepage: \href{https://github.com/ngoldbaum}{https://github.com/ngoldbaum}
\end{minipage}

\section*{Employment}

\subsection*{Recurse Center}
\begin{itemize}
  \item [] \textline{Recurser}{Summer 2019}
\end{itemize}

\subsection*{National Center for Supercomputing Applications}
\begin{itemize}
  \item[] \textline{Research Scientist}{2017 -- 2019}  %chktex 8
  \item[] \textline{Postdoctoral Researcher, Data Exploration Lab}{2015 -- 2017}  %chktex 8
\end{itemize}

\section*{Education}

\subsection*{University of California Santa Cruz}
\emph{Dissertation:} ``Star Formation in Graivtationally Unstable Disk
Galaxies: From Clouds to Disks''\\
\begin{itemize}
\item[] \textline{Ph.D. Astronomy \& Astrophysics}{2011 -- 2015}  %chktex 8
\item[] \textline{NSF Graduate Research Fellow}{2010 -- 2013}  %chktex 8
\item[] \textline{M.S. Astronomy \& Astrophysics}{2009 -- 2011}  %chktex 8
\end{itemize}

\subsection*{University of Colorado Boulder}
\begin{itemize}
  \item[] \textline{B.A. Physics, \textit{Summa Cum Laude}}{2005 -- 2009}  %chktex 8
\end{itemize}

\section*{Open Source Contributions\footnote{See
    \href{https://www.openhub.net/accounts/ngoldbaum}{https://www.openhub.net/accounts/ngoldbaum}
    for a contribution summary}}

\subsection*{yt}
An analysis and visualization toolkit for volumetric data.

\begin{itemize}

\item[] \textline{\bf Core Contributor, Steering Committee Member, and Project Member}{2012 -- 2019}  %chktex 8
  \begin{itemize}
    \item Regularly contributed to project management and planning, including
      design and implementation discussions, code review, and user support on
      IRC and mailing lists.
    \item More than 650 merged pull requests
  \end{itemize}

\item[] \textline{\bf Released \texttt{yt} unit system as a standalone package}{2018 -- 2019}  %chktex 8
  \begin{itemize}
    \item Extracted \texttt{yt.units} module into a standalone package with
      continuous integration, 100\% test coverage, and extensive example-driven
      documentation.
  \end{itemize}

\item[] \textline{\bf Improving support for particle data}{2016 -- 2018}  %chktex 8
  \begin{itemize}
  \item Substantially improved performance and memory usage for common analysis
    tasks.
  \item Presented work to the community at a SciPy conference talk.
  \item Worked with community to provide migration path for analysis results
    requiring data produced by old API.\@
  \end{itemize}

\item[] \textline{\bf Symbolic Unit System}{2013 -- 2014}  %chktex 8
  \begin{itemize}
    \item Designed \texttt{YTArray}, an array data container for automatically
      handling unit conversions and runtime validation for dimensional correctness
      of mathematical operations.
    \item Led the development effort that systematically updated \texttt{yt} to
      make use of the unit system.
  \end{itemize}

\item[] \textline{\bf \texttt{PlotWindow} Plotting Interface}{2012}
  \begin{itemize}
    \item Created an interface for visualizing slices and projections of
      simulation data.
    \item Enables quick data visualization through an API that focuses on what
      the simulation data physically represents rather than how it is laid out
      on disk.
    \item Used in dozens of published journal articles written by
      \texttt{yt} users.
    \item Responsible for the initial design, implementation, documentation, and
      ongoing maintenance.
  \end{itemize}

\end{itemize}

\subsection*{Additional Contributions}

\begin{itemize}
\item[] {\bf Enzo}: High performance parallel astrophysics simulation code,
  contributed more than 50 pull requests
\item[] {\bf Grackle}: Astrophysics thermal chemistry library, Set up an
  automated test suite and continuous integration
\item[] {\bf Matplotlib}: Contributed bugfixes and minor improvements in 11
  merged pull requests.
\item[] {\bf Mercurial}: Several bugfixes and minor improvements.
\item[] {\bf xonsh}: Added integration with the mercurial version control System.
\item[] {\bf Jupyter}: Provided bugfixes and minor improvement to several
  Jupyter projects including \texttt{ipywidgets}, \texttt{IPython}, and
  \texttt{nbconvert}.
\end{itemize}

\section*{First Author Publications}

\begin{itemize}
  \item[] ``\texttt{unyt}: Handle, manipulate, and convert data with physical
    units in Python'', {\bf Goldbaum, N.~J.}, ZuHone, J.~A., Turk, M.~J., et
    al.\ 2018, The Journal of Open Source Software, 3, 809.
  \item[] ``Mass Transport and Turbulence in Gravitationally Unstable Disk
    Galaxies II:\@
    The Effects of Star Formation Feedback'', {\bf Goldbaum, N.~J.}, Krumholz, M.~R., \& Forbes,
    J.~C., {\it Astrophysical Journal}, 2016, 827, 28
  \item[] ``Mass Transport and Turbulence in Gravitationally Unstable Disk
    Galaxies. I:\@
    The Case of Pure Self-Gravity'', {\bf Goldbaum, N.~J.}, Krumholz, M.~R., \& Forbes,
    J.~C., {\it Astrophysical Journal}, 2015, 814, 131
  \item[] ``The Global Evolution of Giant Molecular Clouds II:\@ The Role of
    Accretion'', {\bf Goldbaum, N.~J.}, Krumholz, M.~R., Matzner, C.~D., McKee,
    C.~F.\ {\it Astrophysical Journal}, 2011, 738, 101
  \item[] ``The Intensity Profile of the Solar Supergranulation'', {\bf Goldbaum,
      N.~J.}, Rast, M.~P., Ermolli, I., Sans, J.~S., Berilli, F.\ {\it
      Astrophysical Journal}, 2009, 707, 67

\end{itemize}

\section*{Talks and Proceedings}

\begin{itemize}
\item[] ``The Demeshening: The Next Generation of Particle Support in yt'',
  {\bf Goldbaum, N.~J.}, Lang, M.~M., SciPy, 2017
\item[] ``Domain Specific Visualization'', {\bf Goldbaum, N.~J.}, PlotCon NYC,
  2016
\item[] ``Publicly Releasing a Large Simulation Dataset'', {\bf Goldbaum,
    N.~J.}, Python in Astronomy Conference, 2016
\item[] ``\texttt{yt}: Volumetric Data Analysis'', {\bf Goldbaum, N.~J.} on
  behalf of the \texttt{yt} project, SciPy conference, 2014

\end{itemize}

\end{document}
